---
title: "R Notebook"
output: html_notebook
---


```{r}
#Upload packages
library(tidyverse)
library(here)
library(patchwork)
library(scales)
library(pracma)
library(magrittr)
library(zoo)
library(lubridate)
```

```{r}
# ctd <- read_csv(here("files", "kc10_profs_qc1.csv"))

ctd <- read_csv(here("outputs", "kc10_fzh01_dfo2_pruth_profs_qcs_qcs7_qc1_2025-01-14.csv"))

#import discrete chlorophyll data
chl <- read_csv(here("files", "chl_all_station_2024-10-25.csv"))

#Download CTD data - entire KC10 FZH01, DFO2 dataset (I really could expand to look at dark count consistency, but these are all deep stations)
ctd_phys <- read.csv(here("files_big", "8_binAvg-1734114948350.csv"))

#For some reason the portal cut out the ctd serial number column from the main csv, so porting it in here.
meta <- read.csv(here("files", "ctd-meta-1734115567369.csv"))

```

```{r}
ctd <- ctd %>% 
  mutate(slope = case_when(ctdNum == 18032 & date < "2015-09-01" ~ 0.68,
                           ctdNum == 18032 & date > "2015-09-01" ~ 0.65,
                           ctdNum == 18066 & year < 2017 ~ 0.81,
                           ctdNum == 18066 & year >= 2017 ~ 0.67,
                           ctdNum == 80217 ~ 0.30,
                           ctdNum == 211567 ~ 0.78,
                           ctdNum == 1907467 ~ 0.96)) %>% 
  mutate(flu_sc = flu_cor*slope)
```

```{r}
#For now, just bringing in the CTD serial number, but I may need to pull more

#Isolating the castpk and serial number.
meta <- meta %>% 
  select(Cast.PK, ctdNum = CTD.serial.number, ctdFirm = CTD.firmware.version)

#Joining the CTD information to the dataset.
ctd_phys <- ctd_phys %>% 
  left_join(meta)

#Wrangling CTD profiles, setting date column and renaming columns 
prof <- ctd_phys %>%
  filter(Cast.Direction.Flag == "d") %>% #downcast data
  mutate(date = lubridate::date(Measurement.time)) %>%
  mutate(year = lubridate::year(Measurement.time)) %>%
  select(castpk = Cast.PK,
         Cruise,
         ctdNum,
         ctdFirm,
         station = Station,
         lat = Latitude,
         long = Longitude,
         time = Measurement.time,
         date,
         year,
         dep = Depth..m.,
         pres = Pressure..dbar.,
         sal = Salinity..PSU.,
         temp = Temperature..deg.C.)
```


```{r}
chl_sf <- chl %>% 
  filter(site_id == "KC10") %>% 
  filter(!is.na(chla)) %>%
  filter(chla > 0) %>% 
  filter(chla_flag == "AV" | chla_flag == "SVC" | is.na(chla_flag)) %>%
  filter(!filter_type == "Bulk GF/F") %>% 
  group_by(event_pk, site_id, date, line_out_depth) %>% 
  mutate(n_filt = n()) %>% 
  ungroup() %>% 
  group_by(event_pk, site_id, date, line_out_depth, filter_type) %>% 
  mutate(n_type = n()) %>% 
  ungroup() %>% 
  filter(n_filt == 3 & n_type == 1) %>% 
  group_by(site_id, date, line_out_depth, filter_type) %>% 
  mutate(avg_chla = mean(chla),
            n_dup = n()) %>% 
  ungroup() %>% 
  group_by(site_id, date, line_out_depth) %>% 
  mutate(sum_chl_avg = sum(avg_chla)) %>% 
  ungroup() %>% 
  mutate(dep_diff_sf = line_out_depth - pressure_transducer_depth) %>% 
  select(event_pk, date, site_id, line_out_depth, dep_diff_sf,
         sum_chl_avg) 

chl_sf_dep <- chl_sf %>% 
  distinct() %>% 
  group_by(date) %>% 
  mutate(n = n_distinct(line_out_depth)) %>% 
  ungroup() %>% 
  filter(n == 5) %>% 
  group_by(date) %>% 
  summarise(int_30 = sum(sum_chl_avg)) %>% 
  ungroup() 
```

```{r}
#this plot shows that the 2022 spring bloom was underestimated by the integrated chlorophyll fluorescence - I think. You should plot them together to see where they depart.

#Is there a way to interpolate between depths - yes, but how?
chl_sf_dep %>% 
  ggplot(aes(x = date, y = int_30)) +
  geom_point() +
  geom_line()
```

```{r}
chl_sf_5d <-  chl_sf %>% 
  distinct() %>% 
  group_by(date) %>% 
  mutate(n = n_distinct(line_out_depth)) %>% 
  ungroup() %>% 
  filter(n == 5)

test_date <- chl_sf_5d %>% 
  filter(date == "2019-08-03") %>% 
  select(depth = line_out_depth, chl = sum_chl_avg) %>% 
  mutate(depth = case_when(depth == 0 ~ 1,
                           T ~ as.numeric(depth)))

test_date_ctd <- ctd %>% 
  filter(date == "2019-08-03" & pres < 31 & station == "KC10") %>% 
  group_by(pres) %>% 
  summarise(flu_avg = mean(flu_sc)) %>% 
  ungroup() %>% 
  rename(depth = pres)
```

```{r}
# https://dewey.dunnington.ca/post/2019/depth-time-heatmaps/
#Adding a smooth fit to a discrete chlorophyll profile
smooth_fit <- loess(chl ~ depth, 
  data = test_date, 
  span = 0.5)

#Pulls out the data along the fit using depth range and number of points across range
chl_smooth <-  
  crossing(tibble(depth = seq(1, 30, length.out = 30))) %>%
  mutate(chl_sm = predict(smooth_fit, 
      newdata = tibble(depth = depth)))

#Joining it with the discrete data for comparison.
chl_smooth <- chl_smooth %>% 
  left_join(test_date) %>% 
  left_join(test_date_ctd)

#Plotting to see how well the fit represents the discrete data - bring in the fluorometer data to compare.
ggplot(chl_smooth, aes(y = depth)) +
  geom_line(aes(x = chl_sm), orientation = "y") +
  geom_line(aes(x = flu_avg), orientation = "y") +
  geom_point(aes(x = chl)) +
  geom_point(aes(x = flu_avg)) +
  lims(x = c(0, 2)) +
  theme_bw() +
  scale_y_reverse()

#Definitely not perfect, but trends tend to be similar - not sure why there still appears to be such an offset despite "calibrating the fluorescence"
```





```{r}
#This is all useful, but can't figure out how to do it to each profile. Ideally can recreate my fluorscence depth plot with 

#trying to do interpolation on all of the discrete samples.
x <- chl_sf_5d %>%
  select(event_pk, date, depth = line_out_depth, chl = sum_chl_avg)  

x2 <- x %>%
  mutate(
    day_in_year = as.numeric(date - floor_date(date, unit = "years"), unit = "days"),
    date_label = ymd("2019-01-01") + day_in_year)

smooth_fit <- loess(
  chl ~ day_in_year + depth, 
  data = x2, 
  span = 0.5)

temp_raster_smooth <- crossing(
  tibble(date = seq(ymd("2019-01-01"), ymd("2019-12-31"), by = 1)),
  tibble(depth = seq(1, 30, length.out = 30))
) %>%
  mutate(
    day_in_year = as.numeric(date - floor_date(date, unit = "years"), unit = "days"),
    chl = predict(
      smooth_fit, 
      newdata = tibble(day_in_year = day_in_year, depth = depth)
    )
  )

temp_raster_smooth2 <- temp_raster_smooth %>% 
  mutate(month = month(date)) %>% 
  group_by(month, depth) %>%
  mutate(chl = median(chl, na.rm = T)) %>% 
  ungroup()

ggplot(temp_raster_smooth2, aes(as.factor(month), depth, fill = chl)) +
  geom_raster() +
  scale_y_reverse() +
  scale_fill_gradient2() +
  coord_cartesian(expand = FALSE)
```





```{r}
#Looking at QSC07 versus QCS01 - pivoting wider and removing NAs, which gives days where both were sampled.
comp <- ctd %>% 
  filter(station == "QCS01" |
           station == "QCS07") %>%
  group_by(date, station, pres) %>% 
  summarise(flu_dm = mean(flu_sc)) %>% 
  ungroup() %>% 
  select(date, station, pres, flu_dm) %>% 
  pivot_wider(names_from = "station", values_from = "flu_dm") %>% 
  drop_na()

#Only 3 direct comparison days, but where they exist, not great.
comp %>% 
  pivot_longer(cols = c(QCS01, QCS07), names_to = "station", values_to = "flu_dm") %>% 
  ggplot(aes(x = flu_dm, y = pres, color = station)) +
  geom_line(orientation = "y", size = 2) +
  facet_wrap(~date) +
  scale_y_reverse() +
  theme_bw()

ggsave(here("figures", "compare_qcs_profiles_date_match.png"),
        width = 20, height = 14, dpi = 300)
```

```{r}
#calculating 50m integrated value for each station
int_chl <- ctd %>% 
  select(castpk, station, date, pres, flu_sc) %>%
  filter(pres < 31) %>% 
  group_by(castpk, date) %>% 
  mutate(int_30 = sum(flu_sc, na.rm = T)) %>% 
  ungroup() %>%
  distinct(castpk, station, int_30, .keep_all = T) %>% 
  group_by(date, station) %>% 
  summarise(avg_int = mean(int_30)) %>% 
  ungroup()

test_int <- ctd %>% 
  select(castpk, station, date, pres, flu_sc) %>%
  filter(pres < 31) %>% 
  group_by(castpk, date) %>% 
  mutate(int_30 = trapz(pres, flu_sc)) %>% 
  ungroup() %>%
  distinct(castpk, station, int_30, .keep_all = T) %>% 
  group_by(date, station) %>% 
  summarise(avg_int = mean(int_30)) %>% 
  ungroup()
```


```{r}
int_chl %>% 
  filter(station == "DFO2" | station == "KC10" | station == "QCS01" |
           station == "QCS07") %>% 
  ggplot(aes(x = date, y = avg_int, color = station)) +
  geom_line(size = 2) +
  geom_point(size = 3) +
  scale_x_date(breaks = seq(as.Date("2013-01-01"), as.Date("2025-01-01"),
                            by = "1 year"), date_minor_breaks = "1 month",
               expand = c(0, 0),
               date_labels = "%b%y",
               limits = c(as.Date("2013-01-01"), as.Date("2025-01-01"))) +
  facet_grid(station ~ .) +
  ggsci::scale_colour_npg() +
  theme_bw() +
  labs(y = bquote(CTD[FLU]~"(mg" ~ m^-2*")")) +
  theme(text = element_text(size = 35), #35
        axis.text = element_text(color = "black"),
        axis.title.x = element_blank(),
        legend.position = "none")

ggsave(here("figures", "timeseries_integrated_ctd_fluorescence2_station_slope_correct.png"),
        width = 20, height = 14, dpi = 300)
```

```{r}
int_chl %>% 
  filter(station == "QCS01" |
           station == "QCS07") %>% 
  ggplot(aes(x = date, y = avg_int, color = station)) +
  geom_line(size = 2) +
  geom_point(size = 3) +
  scale_x_date(breaks = seq(as.Date("2013-01-01"), as.Date("2025-01-01"),
                            by = "1 year"), date_minor_breaks = "1 month",
               expand = c(0, 0),
               date_labels = "%b%y",
               limits = c(as.Date("2013-01-01"), as.Date("2025-01-01"))) +
  # facet_grid(station ~ .) +
  ggsci::scale_colour_npg() +
  theme_bw() +
  labs(y = bquote(CTD[FLU]~"(mg" ~ m^-2*")")) +
  theme(text = element_text(size = 35), #35
        axis.text = element_text(color = "black"),
        axis.title.x = element_blank(),
        legend.position = "none")

ggsave(here("figures", "timeseries_integrated_ctd_qcs_compare.png"),
        width = 20, height = 6, dpi = 300)
```

```{r}
#Looking at QSC07 versus QCS01 scatter of fluorescence
comp2 <- int_chl %>% 
  filter(station == "QCS01" |
           station == "QCS07") %>%
  pivot_wider(names_from = "station", values_from = "avg_int") %>% 
  drop_na()

#So very few comparison days, but where they exist, not great.
comp %>% 
  pivot_longer(cols = c(QCS01, QCS07), names_to = "station", values_to = "flu_dm") %>% 
  ggplot(aes(x = flu_dm, y = pres, color = station)) +
  geom_line(orientation = "y", size = 2) +
  facet_wrap(~date) +
  scale_y_reverse() +
  theme_bw()
```



```{r}
test_int %>% 
  filter(station == "DFO2" | station == "KC10" | station == "QCS01") %>% 
  ggplot(aes(x = date, y = avg_int, color = station)) +
  geom_line(size = 2) +
  geom_point(size = 3) +
  scale_x_date(breaks = seq(as.Date("2013-01-01"), as.Date("2025-01-01"),
                            by = "1 year"), date_minor_breaks = "1 month",
               expand = c(0, 0),
               date_labels = "%b%y",
               limits = c(as.Date("2013-01-01"), as.Date("2025-01-01"))) +
  facet_grid(station ~ .) +
  ggsci::scale_colour_npg() +
  theme_bw() +
  labs(y = bquote(CTD[FLU]~"(mg" ~ m^-2*")")) +
  theme(text = element_text(size = 35), #35
        axis.text = element_text(color = "black"),
        axis.title.x = element_blank(),
        legend.position = "none")

ggsave(here("figures", "timeseries_integrated_ctd_fluorescence2_TRAP.png"),
        width = 20, height = 14, dpi = 300)
```

```{r}
prof %>% 
  filter(station == "KC10" & pres == 5) %>% 
  ggplot(aes(x = date, y = sal)) + 
  geom_line() +
  scale_x_date(breaks = seq(as.Date("2012-01-01"), as.Date("2025-01-01"),
                            by = "1 year"), date_minor_breaks = "1 month",
               expand = c(0, 0),
               date_labels = "%b%y",
               limits = c(as.Date("2013-01-01"), as.Date("2025-01-01"))) 
```



#Calculating monthly climatology
```{r}
#Pulling out KC10 for calculations
int_kc10 <- test_int %>% 
  mutate(year = lubridate::year(date),
         month = lubridate::month(date)) %>%
  filter(station == "KC10") %>% 
  mutate(month_adj = case_when(date == "2022-07-28" ~ 8,
                               date == "2017-08-31" ~ 9,
                               date == "2017-04-28" ~ 5,
                               T ~ as.numeric(month)))

#calculate the climatological mean, standard deviation and number of samples in each bin
int_ts_mm <- int_kc10 %>%
  group_by(month_adj) %>% 
  summarise(mm_ts_int = mean(avg_int, na.rm = T),
            sd_ts_int = sd(avg_int, na.rm = T),
            n_ts = n()) %>% 
  ungroup()

#creating a monthly mean for each year - some years have more than 1 observation - I think. I should maybe correct for where there are two observations per month.
int_year_mm <- int_kc10 %>%
  select(year, month_adj, avg_int) %>% 
  group_by(year, month_adj) %>% 
  summarise(mm_year_int = mean(avg_int, na.rm = T),
            n_year = n()) %>% 
  ungroup() 

#calculate the standardized anomaly and create a center of the month date for plotting
int_anomaly_month <- int_year_mm %>% 
  left_join(int_ts_mm) %>% 
  mutate(anom = mm_year_int - mm_ts_int,
         anom_std = anom/sd_ts_int,
         day = 15) %>% 
  unite("date", year, month_adj, day, sep = "-", remove = F) %>% 
  mutate(date2 = lubridate::ymd(date)) %>% 
  mutate(pos = anom >= 0) #allows me to plot red/blue colors
```

```{r}
int_anomaly_month %>% 
  ggplot() +
  geom_area(data = int_kc10, aes(x = date, y = avg_int), alpha = 0.3) +
  geom_col(data = int_anomaly_month, aes(x = date2, y = anom, fill = pos),
           position = "identity", colour = "black") +
  scale_fill_manual(values = c("blue", "red"), guide = FALSE) +
  # geom_hline(yintercept = 1) +
  # geom_hline(yintercept = -1) +
  # geom_hline(yintercept = 2, linetype = "dashed") +
  # geom_hline(yintercept = -2, linetype = "dashed") +
  # lims(y = c(-0.5, 0.5)) +
  scale_x_date(limits = as.Date(c("2012-01-01", "2025-01-01")),
               expand = c(0, 0),
               date_breaks = "years", date_labels = "%b%y") +
  labs(y = bquote(Monthly~Anomaly~"(mg" ~ m^-2*")")) +
  theme_bw() +
  theme(strip.background = element_blank(),
        panel.grid.major.x =  element_line(color = "black", size = 0.5),
        panel.grid.minor.x =  element_line(color = "darkgrey", size = 0.5),
        # strip.text.x = element_blank(),
        # panel.spacing = unit(2, "lines"),
        text = element_text(size = 40),
        axis.text = element_text(colour = "black"),
        axis.title.x = element_blank())

ggsave(here("figures", "anomaly_test.png"),
        width = 20, height = 8, dpi = 300)
```
```{r}
export_int_kc10 <- int_kc10 %>% 
  select(date, year, month, month_adj, int_chl = avg_int)

export_anom_kc10 <- int_anomaly_month %>% 
  select(date, year, month_adj, anom)
```



```{r}
write.csv(export_int_kc10, here("outputs", "kc10_integrated_chl_2025-01-23.csv"))
write.csv(export_anom_kc10, here("outputs", "kc10_anom_chl_2025-01-23.csv"))
```





```{r}
int_chl %>% 
  filter(station == "DFO2" | station == "KC10" | station == "QCS01" |
           station == "QCS07") %>% 
  mutate(month = lubridate::month(date),
         year = lubridate::year(date)) %>% 
  ggplot(aes(x = as.factor(month), y = avg_int, fill = station)) +
  geom_boxplot() +
  facet_grid(station ~ .) +
  ggpubr::stat_compare_means() +
  # geom_point(aes(fill = as.factor(year)), pch = 21, size = 5) +
  # scale_fill_viridis_d() +
  # labs(fill = NULL) +
  ggsci::scale_fill_npg() +
  theme_bw() +
  labs(y = bquote(CTD[FLU]~"(mg" ~ m^-2*")")) +
  theme(text = element_text(size = 35), #35
        axis.text = element_text(color = "black"),
        axis.title.x = element_blank(),
        legend.position = "none")

ggsave(here("figures", "timeseries_integrated_monthly_climatology.png"),
        width = 16, height = 14, dpi = 300)
```
```{r}
test_int %>% 
  filter(station == "DFO2" | station == "KC10" | station == "QCS01") %>% 
  mutate(month = lubridate::month(date),
         year = lubridate::year(date)) %>% 
  ggplot(aes(x = as.factor(month), y = avg_int, fill = station)) +
  geom_boxplot() +
  facet_grid(station ~ .) +
  ggpubr::stat_compare_means() +
  # geom_point(aes(fill = as.factor(year)), pch = 21, size = 5) +
  # scale_fill_viridis_d() +
  # labs(fill = NULL) +
  ggsci::scale_fill_npg() +
  theme_bw() +
  labs(y = bquote(CTD[FLU]~"(mg" ~ m^-2*")")) +
  theme(text = element_text(size = 35), #35
        axis.text = element_text(color = "black"),
        axis.title.x = element_blank(),
        legend.position = "none")

ggsave(here("figures", "timeseries_integrated_monthly_climatology_TRAP.png"),
        width = 16, height = 14, dpi = 300)
```



```{r}
test <- int_chl %>% 
  filter(station == "DFO2" | station == "KC10" | station == "QCS01" |
           station == "QCS07") %>% 
  mutate(station2 = case_when(station == "QCS07" ~ "QCS01",
                              TRUE ~ as.character(station))) %>% 
  mutate(month = lubridate::month(date),
         year = lubridate::year(date))  


ggpubr::ggboxplot(test, x = "month", y = "avg_int",
          color = "black", fill = "station2", palette = "jco", size = 1) +
  facet_grid(station2 ~ .) +
  ggpubr::stat_compare_means(label.y.npc = 0.95, size = 7) +
  ggpubr::stat_compare_means(label = "p.signif",
                     ref.group = ".all.", hide.ns = TRUE,
                     label.y.npc = 0.82, size = 13, 
                     color = "blue") +
  theme_bw() +
  labs(y = bquote(CTD[FLU]~"(mg" ~ m^-2*")")) +
  theme(text = element_text(size = 35), #35
        axis.text = element_text(color = "black"),
        axis.title.x = element_blank(),
        legend.position = "none")

ggsave(here("figures", "timeseries_integrated_monthly_climatology_stat_mash_qc7.png"),
        width = 16, height = 14, dpi = 300)
```
```{r}
scm_max <- ctd %>%
  filter(station == "KC10" | station == "QCS01" | station == "DFO2" | 
           station == "QSC07") %>% 
  group_by(castpk) %>% 
  top_n(flu_sc, n = 1) %>% 
  select(castpk, date, station, max_flu_dep = pres, max_flu = flu_sc)

int_chl <- int_chl %>% 
  filter(station == "KC10" | station == "QCS01" | station == "DFO2" | 
           station == "QSC07") %>% 
  left_join(scm_max) %>% 
  mutate(scm_rat = avg_int/max_flu,
         month = lubridate::month(date)) 
```

```{r}
ggpubr::ggboxplot(int_chl, x = "month", y = "scm_rat",
          color = "black", fill = "station", palette = "jco", size = 1) +
  facet_grid(station ~ .) +
  ggpubr::stat_compare_means(label.y.npc = 0.95, size = 7) +
  ggpubr::stat_compare_means(label = "p.signif",
                     ref.group = ".all.", hide.ns = TRUE,
                     label.y.npc = 0.82, size = 13,
                     color = "blue") +
  theme_bw() +
  labs(y = bquote(SCM[RATIO])) +
  theme(text = element_text(size = 35), #35
        axis.text = element_text(color = "black"),
        axis.title.x = element_blank(),
        legend.position = "none")

ggsave(here("figures", "timeseries_scm-ratio_monthly_climatology.png"),
        width = 16, height = 14, dpi = 300)
```











```{r}
ggpubr::ggboxplot(test, x = "month", y = "avg_int",
          color = "black", fill = "station", palette = "jco", size = 1) +
  # facet_grid(station ~ .) +
  ggpubr::stat_compare_means(aes(group = station), label = "p.signif",
                             hide.ns = TRUE,
                             label.y.npc = 0.95, 
                             size = 10, 
                             color = "blue") +
  # ggpubr::stat_compare_means(aes(group = station), label = "p.signif",
  #                    ref.group = ".all.", hide.ns = TRUE,
  #                    label.y.npc = 0.82, size = 13, 
  #                    color = "blue") +
  theme_bw() +
  labs(y = bquote(CTD[FLU]~"(mg" ~ m^-2*")")) +
  theme(text = element_text(size = 35), #35
        axis.text = element_text(color = "black"),
        axis.title.x = element_blank(),
        legend.position = "none")

ggsave(here("figures", "timeseries_integrated_monthly_climatology_station_stat.png"),
        width = 16, height = 6, dpi = 300)
```






```{r}
int_chl %>% 
  filter(station == "DFO2" | station == "KC10" | station == "QCS01") %>% 
  mutate(month = lubridate::month(date),
         year = lubridate::year(date)) %>% 
  ggplot(aes(x = as.factor(month), y = avg_int, fill = station)) +
  geom_boxplot() +
  # geom_point(aes(fill = as.factor(year)), pch = 21, size = 5) +
  # scale_fill_viridis_d() +
  labs(fill = NULL) +
  ggsci::scale_fill_npg() +
  theme_bw() +
  labs(y = bquote(CTD[FLU]~"(mg" ~ m^-2*")")) +
  theme(text = element_text(size = 35), #35
        axis.text = element_text(color = "black"),
        axis.title.x = element_blank(),
        legend.position = c(0.9, 0.85))

ggsave(here("figures", "timeseries_integrated_monthly_climatology_single.png"),
        width = 16, height = 6, dpi = 300)
```


```{r}
ctd_dm <- ctd %>% 
  filter(pres >= 0 & pres <= 50) %>% 
  group_by(date, station, pres) %>% 
  summarise(flu_sc_dm = mean(flu_sc)) %>% 
  ungroup()

formatter <- function(...){
  function(x) format(round(x, 1), ...)
}

ctd_dm %>% 
  mutate(month = lubridate::month(date),
         year = lubridate::year(date)) %>% 
  filter(month > 2 & month < 11) %>% 
  filter(station == "DFO2" | station == "KC10" | station == "QCS01") %>% 
  ggplot(aes(y = pres, x = flu_sc_dm)) +
  geom_line(aes(group = date, color = as.factor(year)),
            orientation = "y", size = 2) +
  geom_vline(xintercept = 5) +
  facet_grid(station ~ month, scales = "free_x") +
  scale_y_reverse() +
  # ylim(50, 0) +
  labs(x = bquote("CTD Fluorescence (mg"~m^-3*")"),
       y = "Depth (m)") +
  theme_bw() +
  scale_color_viridis_d() +
  scale_x_continuous(limits = c(0, NA), expand = c(0, 0), 
                     labels = formatter(nsmall = 1)) +
  theme_bw() +
  theme(strip.background = element_blank(),
        text = element_text(size = 25),
        axis.text = element_text(colour = "black"),
        legend.title = element_blank(),
        # legend.position = c(0.07, 0.95),
        panel.spacing.x = unit(2, "lines"))

ggsave(here("figures", "ctd_profiles_all.png"),
        width = 27, height = 14, dpi = 300)
```
```{r}
ctd %>% 
  mutate(month = lubridate::month(date),
         year = lubridate::year(date)) %>% 
  filter(month > 2 & month < 11) %>% 
  filter(station == "DFO2" | station == "KC10" | station == "QCS01") %>%
  filter(pres >= 0 & pres <= 50) %>%
  group_by(month, station, pres) %>%
  mutate(flu_med = median(flu_sc, na.rm = T)) %>% 
  ungroup() %>% 
  ggplot() +
  geom_line(aes(y = pres, x = flu_med), orientation = "y", size = 2,
            color = "black") +
  geom_vline(xintercept = 5) +
  facet_grid(station ~ month) +
  scale_y_reverse() +
  # ylim(50, 0) +
  labs(x = bquote("CTD Fluorescence (mg"~m^-3*")"),
       y = "Depth (m)") +
  theme_bw() +
  scale_color_viridis_c() +
  scale_x_continuous(limits = c(0, NA), expand = c(0, NA), 
                     labels = formatter(nsmall = 1)) +
  theme_bw() +
  theme(strip.background = element_blank(),
        text = element_text(size = 30),
        axis.text = element_text(colour = "black"),
        legend.title = element_blank(),
        # legend.position = c(0.07, 0.95),
        panel.spacing.x = unit(2, "lines"))

ggsave(here("figures", "ctd_profiles_median_season.png"),
        width = 27, height = 14, dpi = 300)
```

```{r}
test2 <- ctd %>% 
  mutate(month = lubridate::month(date),
         year = lubridate::year(date)) %>% 
  filter(station == "DFO2" | station == "KC10" | station == "QCS01" | 
           station == "QCS07") %>%
  mutate(station2 = case_when(station == "QCS07" ~ "QCS01",
                              TRUE ~ as.character(station))) %>% 
  filter(pres >= 0 & pres <= 30) %>%
  group_by(month, station2, pres) %>%
  mutate(flu_med = median(flu_sc, na.rm = T),
         var_flu = var(flu_sc, na.rm = T)) %>% 
  ungroup() %>% 
  group_by(month, station2) %>%
  mutate(n_prof = n_distinct(castpk)) %>% 
  ungroup()

test_sal <- prof %>% 
  mutate(month = lubridate::month(date),
         year = lubridate::year(date)) %>% 
  filter(station == "KC10") %>%
  filter(pres >= 0 & pres <= 30) %>%
  group_by(month, station, pres) %>%
  mutate(sal_med = median(sal, na.rm = T),
         var_sal = var(sal, na.rm = T)) %>% 
  ungroup() %>% 
  group_by(month, station) %>%
  mutate(n_prof = n_distinct(castpk)) %>% 
  ungroup()

test3 <- ctd %>%
  mutate(month = lubridate::month(date),
         year = lubridate::year(date)) %>% 
  distinct(castpk, .keep_all = T) %>% 
  group_by(month, station) %>%
  summarise(n_prof = n()) %>% 
  ungroup()
```

```{r}
test2 %>% 
  ggplot() +
  geom_tile(aes(x = as.factor(month), y = pres, fill = flu_med)) +
  geom_text(aes(x = as.factor(month), y = 28, label = n_prof),
            color = "white", size  = 8) +
  # geom_hline(yintercept = 5, color = "white", linetype = "dotted") +
  # geom_hline(yintercept = 10, color = "white", linetype = "dotted") +
  # geom_hline(yintercept = 20, color = "white", linetype = "dotted") +
  # geom_hline(yintercept = 30, color = "white", linetype = "dotted") +
  scale_y_reverse() +
  facet_grid(station2 ~ .) +
  scale_fill_viridis_c(option = "H") +
  theme_bw() +
  labs(fill = bquote(CTD[FLU]~"(mg" ~ m^-3*")"),
       y = "Depth") +
  theme(text = element_text(size = 35), #35
        axis.text = element_text(color = "black"),
        axis.title.x = element_blank(),
        legend.position = "top",
        legend.box = "horizontal") +
  guides(fill = guide_colourbar(title.position = "top", title.hjust = 0.5,
                                barwidth = 50, barheight = 1,
                                frame.colour = "black", ticks.colour = "black"))

ggsave(here("figures", "timeseries_monthly_profile_mash_qc7.png"),
        width = 16, height = 12, dpi = 300)
```
```{r}
f1 <- test2 %>% 
  filter(station == "KC10") %>% 
  ggplot() +
  geom_tile(aes(x = as.factor(month), y = pres, fill = flu_med)) +
  geom_text(aes(x = as.factor(month), y = 28, label = n_prof),
            color = "white", size  = 8) +
  # geom_hline(yintercept = 5, color = "white", linetype = "dotted") +
  # geom_hline(yintercept = 10, color = "white", linetype = "dotted") +
  # geom_hline(yintercept = 20, color = "white", linetype = "dotted") +
  # geom_hline(yintercept = 30, color = "white", linetype = "dotted") +
  scale_y_reverse() +
  # facet_grid(station2 ~ .) +
  scale_fill_viridis_c(option = "H") +
  theme_bw() +
  labs(fill = bquote(CTD[FLU]~"(mg" ~ m^-3*")"),
       y = "Depth") +
  theme(text = element_text(size = 35), #35
        axis.text = element_text(color = "black"),
        axis.title.x = element_blank(),
        legend.position = "top",
        legend.box = "horizontal") +
  guides(fill = guide_colourbar(title.position = "top", title.hjust = 0.5,
                                barwidth = 50, barheight = 1,
                                frame.colour = "black", ticks.colour = "black"))

ggsave(here("figures", "timeseries_monthly_profile_mash_qc7.png"),
        width = 16, height = 12, dpi = 300)
```







```{r}
f2 <- test_sal %>% 
  ggplot() +
  geom_tile(aes(x = as.factor(month), y = pres, fill = sal_med)) +
  geom_text(aes(x = as.factor(month), y = 28, label = n_prof),
            color = "white", size  = 8) +
  # geom_hline(yintercept = 5, color = "white", linetype = "dotted") +
  # geom_hline(yintercept = 10, color = "white", linetype = "dotted") +
  # geom_hline(yintercept = 20, color = "white", linetype = "dotted") +
  # geom_hline(yintercept = 30, color = "white", linetype = "dotted") +
  scale_y_reverse() +
  # facet_grid(station2 ~ .) +
  scale_fill_viridis_c(option = "H", limits = c(25, 32)) +
  theme_bw() +
  labs(fill = "Salinity",
       y = "Depth") +
  theme(text = element_text(size = 35), #35
        axis.text = element_text(color = "black"),
        axis.title.x = element_blank(),
        legend.position = "bottom",
        legend.box = "horizontal") +
  guides(fill = guide_colourbar(title.position = "top", title.hjust = 0.5,
                                barwidth = 50, barheight = 1,
                                frame.colour = "black", ticks.colour = "black"))

ggsave(here("figures", "timeseries_monthly_profile_salinity_KC10.png"),
        width = 16, height = 12, dpi = 300)
```

```{r}
fig <- f1 / f2

ggsave(here("figures", "timeseries_monthly_profile_salinity_flu_KC10.png"), fig,
        width = 16, height = 12, dpi = 300)
```


```{r}
test2 %>% 
  ggplot() +
  geom_tile(aes(x = as.factor(month), y = pres, fill = var_flu)) +
  # geom_hline(yintercept = 5, color = "white", linetype = "dotted") +
  # geom_hline(yintercept = 10, color = "white", linetype = "dotted") +
  # geom_hline(yintercept = 20, color = "white", linetype = "dotted") +
  # geom_hline(yintercept = 30, color = "white", linetype = "dotted") +
  scale_y_reverse() +
  facet_grid(station2 ~ .) +
  scale_fill_viridis_c(option = "H") +
  theme_bw() +
  labs(fill = "Variance",
       y = "Depth") +
  theme(text = element_text(size = 35), #35
        axis.text = element_text(color = "black"),
        axis.title.x = element_blank(),
        legend.position = "top",
        legend.box = "horizontal") +
  guides(fill = guide_colourbar(title.position = "top", title.hjust = 0.5,
                                barwidth = 50, barheight = 1,
                                frame.colour = "black", ticks.colour = "black"))

ggsave(here("figures", "timeseries_monthly_profile_sample_depth_variance_mash_qc7.png"),
        width = 16, height = 12, dpi = 300)
```
```{r}
ctd_kc10 <- ctd %>% 
  mutate(month = lubridate::month(date),
         year = lubridate::year(date)) %>% 
  filter(station == "KC10") %>%
  filter(pres >= 0 & pres <= 30) %>%
  ungroup() 

ctd_kc10_phys <- prof %>% 
  mutate(month = lubridate::month(date),
         year = lubridate::year(date)) %>% 
  filter(station == "KC10") %>%
  filter(pres >= 0 & pres <= 30) %>%
  ungroup() 
  
ctd_kc10_max <- ctd_kc10 %>% 
  group_by(castpk) %>% 
  top_n(flu_sc, n = 1) %>% 
  select(castpk, date, station, max_flu_dep = pres, max_flu = flu_sc)

int_kc10 <- int_kc10 %>% 
  left_join(ctd_kc10_max) %>% 
  mutate(scm_rat = avg_int/max_flu)

ctd_kc10 <- ctd_kc10 %>% 
  left_join(ctd_kc10_max) %>% 
  group_by(year, month, pres) %>%
  summarise(flu_sc = median(flu_sc),
            max_flu = median(max_flu)) %>% 
  ungroup() 
```

```{r}
ggpubr::ggboxplot(int_kc10, x = "month", y = "scm_rat",
          color = "black", fill = "station", palette = "jco", size = 1) 
  ggpubr::stat_compare_means(label.y.npc = 0.95, size = 7) +
  ggpubr::stat_compare_means(label = "p.signif",
                     ref.group = ".all.", hide.ns = TRUE,
                     label.y.npc = 0.82, size = 13, 
                     color = "blue") +
  theme_bw() +
  labs(y = bquote(CTD[FLU]~"(mg" ~ m^-2*")")) +
  theme(text = element_text(size = 35), #35
        axis.text = element_text(color = "black"),
        axis.title.x = element_blank(),
        legend.position = "none")
```





```{r}
ctd_kc10 %>% 
  ggplot(aes(x = as.factor(month))) +
  geom_tile(aes(y = pres, fill = flu_sc)) +
  geom_point(aes(y = max_flu), pch = 21, size = 2, fill = "white") +
  # geom_text(aes(x = as.factor(month), y = 28, label = n_prof),
  #           color = "white", size  = 8) +
  # geom_hline(yintercept = 5, color = "white", linetype = "dotted") +
  # geom_hline(yintercept = 10, color = "white", linetype = "dotted") +
  # geom_hline(yintercept = 20, color = "white", linetype = "dotted") +
  # geom_hline(yintercept = 30, color = "white", linetype = "dotted") +
  scale_y_reverse() +
  facet_wrap(~year) +
  scale_fill_viridis_c(option = "H") +
  theme_bw() +
  labs(fill = bquote(CTD[FLU]~"(mg" ~ m^-3*")"),
       y = "Depth") +
  theme(text = element_text(size = 35), #35
        axis.text = element_text(color = "black"),
        axis.title.x = element_blank(),
        legend.position = "top",
        legend.box = "horizontal") +
  guides(fill = guide_colourbar(title.position = "top", title.hjust = 0.5,
                                barwidth = 50, barheight = 1,
                                frame.colour = "black", ticks.colour = "black"))

ggsave(here("figures", "timeseries_yearly_profile.png"),
        width = 20, height = 20, dpi = 300)
```
```{r}
ctd_kc10_phys %>% 
  ggplot(aes(x = as.factor(month))) +
  geom_tile(aes(y = pres, fill = sal)) +

  # geom_text(aes(x = as.factor(month), y = 28, label = n_prof),
  #           color = "white", size  = 8) +
  # geom_hline(yintercept = 5, color = "white", linetype = "dotted") +
  # geom_hline(yintercept = 10, color = "white", linetype = "dotted") +
  # geom_hline(yintercept = 20, color = "white", linetype = "dotted") +
  # geom_hline(yintercept = 30, color = "white", linetype = "dotted") +
  scale_y_reverse() +
  facet_wrap(~year) +
  scale_fill_viridis_c(option = "H", limits = c(20, 32)) +
  theme_bw() +
  labs(fill = "Salinity",
       y = "Depth") +
  theme(text = element_text(size = 35), #35
        axis.text = element_text(color = "black"),
        axis.title.x = element_blank(),
        legend.position = "top",
        legend.box = "horizontal") +
  guides(fill = guide_colourbar(title.position = "top", title.hjust = 0.5,
                                barwidth = 50, barheight = 1,
                                frame.colour = "black", ticks.colour = "black"))

ggsave(here("figures", "timeseries_yearly_profile_SAL.png"),
        width = 20, height = 20, dpi = 300)
```




```{r}
ctd_kc10 %>% 
  ggplot(aes(x = as.factor(month))) +
  geom_tile(aes(y = pres, fill = flu_sc)) +
  geom_point(aes(y = max_flu), pch = 21, size = 2, fill = "white") +
  # geom_text(aes(x = as.factor(month), y = 28, label = n_prof),
  #           color = "white", size  = 8) +
  # geom_hline(yintercept = 5, color = "white", linetype = "dotted") +
  # geom_hline(yintercept = 10, color = "white", linetype = "dotted") +
  # geom_hline(yintercept = 20, color = "white", linetype = "dotted") +
  # geom_hline(yintercept = 30, color = "white", linetype = "dotted") +
  scale_y_reverse() +
  facet_wrap(~year) +
  scale_fill_viridis_c(option = "H") +
  theme_bw() +
  labs(fill = bquote(CTD[FLU]~"(mg" ~ m^-3*")"),
       y = "Depth") +
  theme(text = element_text(size = 35), #35
        axis.text = element_text(color = "black"),
        axis.title.x = element_blank(),
        legend.position = "top",
        legend.box = "horizontal") +
  guides(fill = guide_colourbar(title.position = "top", title.hjust = 0.5,
                                barwidth = 50, barheight = 1,
                                frame.colour = "black", ticks.colour = "black"))

ggsave(here("figures", "timeseries_yearly_profile.png"),
        width = 20, height = 20, dpi = 300)
```


```{r}
# test2 %>% 
#   mutate(precip_rescaled = precip/200 ,
#          nivel_rescaled = -nivel + 2.5) %>%
#   ggplot() +
#   geom_tile(aes(x = as.factor(month), y = pres, fill = flu_med)) +
#   geom_hline(yintercept = 5, color = "white", linetype = "dotted") +
#   geom_hline(yintercept = 10, color = "white", linetype = "dotted") +
#   geom_hline(yintercept = 20, color = "white", linetype = "dotted") +
#   geom_hline(yintercept = 30, color = "white", linetype = "dotted") +
#   scale_y_reverse() +
#   facet_grid(station ~ .) +
#   scale_fill_viridis_c(option = "H") +
#   theme_bw() +
#   labs(fill = bquote(CTD[FLU]~"(mg" ~ m^-3*")"),
#        y = "Depth") +
#   theme(text = element_text(size = 35), #35
#         axis.text = element_text(color = "black"),
#         axis.title.x = element_blank(),
#         legend.position = "top",
#         legend.box = "horizontal") +
#   guides(fill = guide_colourbar(title.position = "top", title.hjust = 0.5,
#                                 barwidth = 50, barheight = 1,
#                                 frame.colour = "black", ticks.colour = "black"))
# 
# ggsave(here("figures", "timeseries_monthly_profile_sample_depth.png"),
#         width = 16, height = 12, dpi = 300)
```




```{r}


# Perhaps the easiest way to achieve this is to "fake" the primary axis in the same way that you fake the secondary axis. That way, you don't need the added complication of scale_y_reverse:

# library(tidyverse)
# library(scales)
# library(lemon)
# 
# base_nivelprecip %>%
#   mutate(nivel = as.double(nivel),
#          precip = as.double(precip),
#          data = as.POSIXct(data, format = "%m/%d/%Y")) %>% 
#   mutate(precip_rescaled = precip/200 ,
#          nivel_rescaled = -nivel + 2.5) %>% 
#   ggplot(aes(x = data, y = nivel_rescaled,
#              xmin = as.POSIXct("2012-05-01", "%Y-%m-%d"), 
#              xmax = as.POSIXct("2020-04-30",  "%Y-%m-%d"))) +
# 
#   geom_col(aes(x = data, y = precip_rescaled), 
#            colour = '#8D8DAA', size = 1) +
#   geom_line(color = '#041562', size = 0.3) +
#   labs(x = "", y = "Groundwater level (m)") +
#   scale_y_continuous(labels = function(x) -(x - 2.5), limits = c(0, 2.5),
#                   sec.axis = sec_axis(~.*200, 
#                                       name = "Precipitation (mm)")) +
#   lemon::facet_rep_wrap(~poco, nrow = 3, repeat.tick.labels = TRUE) +
#   theme_bw() +
#   theme(text=element_text(size=12),
#         axis.text.x = element_text(size = 8))
```


```{r}
#How could I look at years with high subsurface maxima at KC10.
```













```{r}
int_chl_merge <- int_chl %>% 
  mutate(station = "KC10")

int_chl_r1_merge <- int_chl_r1 %>% 
  mutate(station = "RVRS01")

int_merge <- rbind(int_chl_merge, int_chl_r1_merge)
```

```{r}
int_chl_merge <- int_merge %>% 
  mutate(month = lubridate::month(date),
         year = lubridate::year(date)) %>% 
  ggplot(aes(x = as.factor(month), y = avg_int, fill = station)) +
  geom_boxplot() +
  labs(fill = NULL) +
  ggsci::scale_fill_npg() +
  theme_bw() +
  labs(y = bquote(CTD[FLU]~"(mg" ~ m^-2*")")) +
  theme(text = element_text(size = 35), #35
        axis.text = element_text(color = "black"),
        axis.title.x = element_blank(),
        legend.position = c(0.93, 0.9))

ggsave(here("figures", "timeseries_integrated_monthly_climatology_kc10_rvrs1.png"),
        width = 16, height = 7, dpi = 300)
```



```{r}
ctd <- ctd %>%
  mutate(month = lubridate::month(date),
         year = lubridate::year(date)) %>% 
  mutate(season = case_when(month == 12 | month == 1 | month == 2 ~ "Winter",
                            month >= 3 & month <= 5 ~ "Spring",
                            month >= 6 & month <= 8 ~ "Summer",
                            month >= 9 & month <= 12 ~ "Autumn",)) %>%
  relocate(season, .after = month)    
  
#I want to push December from each year to winter of the next year
ctd <- ctd %>%
  mutate(year = case_when(season == "Winter" & month == 12 ~ year+1,
                           TRUE ~ as.numeric(year)))

#Order locations from fjord to shelf
order_loc_seas <- c("Winter", "Spring", "Summer", "Autumn")

#Chemtax - Specify order of phyto groups for figures
ctd <- arrange(mutate(ctd,
                         season = factor(season, levels = order_loc_seas)))
```

```{r}
formatter <- function(...){
  function(x) format(round(x, 1), ...)
}

ctd_dm <- ctd %>% 
  filter(pres >= 0 & pres <= 50) %>% 
  group_by(date, pres) %>% 
  summarise(flu = mean(flu)) %>% 
  ungroup()

ctd_dm %>% 
  mutate(month = lubridate::month(date),
         year = lubridate::year(date)) %>% 
  filter(month > 4 & month < 9) %>% 
  ggplot(aes(y = pres, x = flu)) +
  geom_line(aes(group = date, color = as.factor(year)),
            orientation = "y", size = 2) +
  facet_grid(. ~ month, scales = "free_x") +
  scale_y_reverse() +
  ylim(50, 0) +
  labs(x = bquote("CTD Fluorescence (mg"~m^-3*")"),
       y = "Depth (m)") +
  theme_bw() +
  scale_color_viridis_d() +
  scale_x_continuous(limits = c(0, NA), expand = c(0, 0), 
                     labels = formatter(nsmall = 1)) +
  theme_bw() +
  theme(strip.background = element_blank(),
        text = element_text(size = 25),
        axis.text = element_text(colour = "black"),
        legend.title = element_blank(),
        # legend.position = c(0.07, 0.95),
        panel.spacing.x = unit(2, "lines"))

ggsave(here("figures", "ctd_profiles_2.png"),
        width = 16, height = 13, dpi = 300)
```

```{r}
dino_prof <- ctd %>% 
  filter(date == "2022-07-28" | date == "2021-08-05") %>% 
  filter(pres < 50) %>% 
  select(date, pres, flu, sal, temp) %>% 
  pivot_longer(c(flu:temp), names_to = "par", values_to = "val") %>% 
  group_by(date, par, pres) %>% 
  summarise(val_avg = mean(val)) %>% 
  ungroup() 
  
dino_prof %>% 
  filter(date == "2022-07-28") %>%
  ggplot(aes(y = pres, x = val_avg)) +
  geom_line(aes(group = date),
            orientation = "y", size = 2) +
  facet_grid(. ~ par, scales = "free") +
  scale_y_reverse() +
  ylim(50, 0) +
  labs(
    # x = bquote("CTD Fluorescence (mg"~m^-3*")"),
       y = "Depth (m)") +
  theme_bw() +
  scale_color_viridis_d() +
  scale_x_continuous(
    # limits = c(0, NA), expand = c(0, 0),
                     labels = formatter(nsmall = 1)) +
  theme_bw() +
  theme(strip.background = element_blank(),
        text = element_text(size = 25),
        axis.text = element_text(colour = "black"),
        legend.title = element_blank(),
        # legend.position = c(0.07, 0.95),
        panel.spacing.x = unit(2, "lines"))  

ggsave(here("figures", "ctd_profiles_dino.png"),
        width = 12, height = 10, dpi = 300)
```




```{r}
ctd_dm_r1 <- ctd_r1 %>% 
  filter(pres >= 0 & pres <= 50) %>% 
  group_by(date, pres) %>% 
  summarise(flu = mean(flu)) %>% 
  ungroup()

ctd_dm_r1 %>% 
  mutate(month = lubridate::month(date),
         year = lubridate::year(date)) %>% 
  filter(month > 2 & month < 9) %>% 
  ggplot(aes(y = pres, x = flu)) +
  geom_line(aes(group = date, color = as.factor(year)),
            orientation = "y", size = 2) +
  facet_grid(. ~ month, scales = "free_x") +
  scale_y_reverse() +
  ylim(50, 0) +
  labs(x = bquote("CTD Fluorescence (mg"~m^-3*")"),
       y = "Depth (m)") +
  theme_bw() +
  scale_color_viridis_d() +
  scale_x_continuous(limits = c(0, NA), expand = c(0, 0), 
                     labels = formatter(nsmall = 1)) +
  theme_bw() +
  theme(strip.background = element_blank(),
        text = element_text(size = 25),
        axis.text = element_text(colour = "black"),
        legend.title = element_blank(),
        # legend.position = c(0.07, 0.95),
        panel.spacing.x = unit(2, "lines"))

ggsave(here("figures", "ctd_profiles_rvrs01.png"),
        width = 16, height = 13, dpi = 300)
```







```{r}
ctd %>% 
  filter(pres >= 0 & pres <= 50) %>%
  mutate(lubridate::month(date)) %>% 
  group_by(season, pres) %>%
  mutate(flu_med = median(flu, na.rm = T)) %>% 
  ungroup() %>% 
  ggplot() +
  geom_line(aes(y = pres, x = log1p(flu), group = castpk, color = year),
            orientation = "y", size = 0.5,
            color = "grey"
            ) +
  geom_line(aes(y = pres, x = flu_med), orientation = "y", size = 2,
            color = "black") +
  facet_grid(. ~ season) +
  scale_y_reverse() +
  ylim(50, 0) +
  labs(x = bquote("CTD Fluorescence (mg"~m^-3*")"),
       y = "Depth (m)") +
  theme_bw() +
  scale_color_viridis_c() +
  scale_x_continuous(limits = c(0, NA), expand = c(0, NA), 
                     labels = formatter(nsmall = 1)) +
  theme_bw() +
  theme(strip.background = element_blank(),
        text = element_text(size = 35),
        axis.text = element_text(colour = "black"),
        legend.title = element_blank(),
        # legend.position = c(0.07, 0.95),
        panel.spacing.x = unit(2, "lines"))

ggsave(here("figures", "ctd_profiles_median_season.png"),
        width = 16, height = 13, dpi = 300)
```

```{r}
ctd %>% 
  filter(pres >= 0 & pres <= 50) %>%
  mutate(lubridate::month(date)) %>%
  filter(season == "Spring" | season == "Summer") %>% 
  group_by(month, pres) %>%
  mutate(flu_med = median(flu, na.rm = T)) %>% 
  ungroup() %>% 
  ggplot() +
  geom_line(aes(y = pres, x = log1p(flu), group = castpk, color = year),
            orientation = "y", size = 0.5,
            color = "grey"
            ) +
  geom_line(aes(y = pres, x = flu_med), orientation = "y", size = 2,
            color = "black") +
  facet_grid(. ~ month) +
  scale_y_reverse() +
  ylim(50, 0) +
  labs(x = bquote("CTD Fluorescence (mg"~m^-3*")"),
       y = "Depth (m)") +
  theme_bw() +
  scale_color_viridis_c() +
  scale_x_continuous(limits = c(0, NA), expand = c(0, NA), 
                     labels = formatter(nsmall = 1)) +
  theme_bw() +
  theme(strip.background = element_blank(),
        text = element_text(size = 35),
        axis.text = element_text(colour = "black"),
        legend.title = element_blank(),
        # legend.position = c(0.07, 0.95),
        panel.spacing.x = unit(2, "lines"))

ggsave(here("figures", "ctd_profiles_median_month_spring_summer.png"),
        width = 16, height = 13, dpi = 300)
```






```{r}
ctd %>% 
  filter(pres >= 0 & pres <= 50 & year == 2013) %>% 
  ggplot(aes(y = pres, x = flu)) +
  geom_line(aes(group = castpk, color = year),
            orientation = "y", size = 1) +
  facet_grid(. ~ season, scales = "free_x") +
  scale_y_reverse() +
  ylim(50, 0) +
  labs(x = bquote("CTD Fluorescence (mg"~m^-3*")"),
       y = "Depth (m)") +
  theme_bw() +
  scale_color_viridis_c() +
  scale_x_continuous(limits = c(0, NA), 
                     labels = formatter(nsmall = 1)) +
  theme_bw() +
  theme(strip.background = element_blank(),
        text = element_text(size = 25),
        axis.text = element_text(colour = "black"),
        legend.title = element_blank(),
        # legend.position = c(0.07, 0.95),
        panel.spacing.x = unit(2, "lines"))

ggsave(here("figures", "ctd_profiles_2013.png"),
        width = 16, height = 13, dpi = 300)
```

```{r}
ctd_2023 <- ctd %>% 
  filter(pres >= 0 & pres <= 50 & year == 2023)  
```




```{r}
ctd_max <- ctd %>% 
  filter(pres <= 30) %>% 
  group_by(castpk) %>% 
  filter(flu == max(flu)) %>% 
  ungroup() %>% 
  group_by(date) %>% 
  summarise(med_max = median(pres)) %>% 
  ungroup() %>% 
  mutate(month = lubridate::month(date),
         station = "KC10")

ctd_max_r1 <- ctd_r1 %>% 
  filter(pres <= 30) %>% 
  group_by(castpk) %>% 
  filter(flu == max(flu)) %>% 
  ungroup() %>% 
  group_by(date) %>% 
  summarise(med_max = median(pres)) %>% 
  ungroup() %>% 
  mutate(month = lubridate::month(date),
         station = "RVRS01")

ctd_max_merge <- rbind(ctd_max, ctd_max_r1)
```

```{r}
max_box <- ctd_max %>% 
  ggplot(aes(x = as.factor(month), y = med_max)) +
  geom_boxplot() +
  scale_y_reverse() +
  theme_bw() +
  labs(y = bquote(Max[FLU]~"(Depth" ~ m^-1*")")) +
  theme(text = element_text(size = 35), #35
        axis.text = element_text(color = "black"),
        axis.title.x = element_blank())

ggsave(here("figures", "timeseries_chla_max_depth.png"),
        width = 16, height = 7, dpi = 300)
```

```{r}
max_box_merge <- ctd_max_merge %>% 
  ggplot(aes(x = as.factor(month), y = med_max, fill = station)) +
  geom_boxplot() +
  scale_y_reverse() +
  ggsci::scale_fill_npg() +
  theme_bw() +
  labs(y = bquote(Max[FLU]~"(Depth" ~ m^-1*")")) +
  theme(text = element_text(size = 35), #35
        axis.text = element_text(color = "black"),
        axis.title.x = element_blank(),
        legend.position = "none")

ggsave(here("figures", "timeseries_chla_max_depth_kc10_rvrs01.png"),
        width = 16, height = 7, dpi = 300)
```

```{r}
int_dep <- int_box / max_box

int_dep_merge <- int_chl_merge/max_box_merge

ggsave(here("figures", "box_monthly_int_max_clim.png"), int_dep,
        width = 16, height = 12, dpi = 300)

ggsave(here("figures", "box_monthly_int_max_clim_kc10_rvrs01.png"), int_dep_merge,
        width = 16, height = 12, dpi = 300)
```



```{r}
ctd_2016 <- ctd %>% 
  filter(year == 2016 & season == "Summer")

ctd_2016_ex <- ctd_2016 %>% 
  filter(date == "2016-06-30")

ctd_2016_ex %>% 
  ggplot() +
  geom_line(aes(y = pres, x = sal, group = castpk), orientation = "y", size = 2,
            color = "black") +
  scale_y_reverse() +
  ylim(50, 0) +
  labs(x = bquote("CTD Fluorescence (mg"~m^-3*")"),
       y = "Depth (m)") +
  theme_bw() +
  scale_color_viridis_c() +
  # scale_x_continuous(limits = c(0, NA), expand = c(0, NA), 
  #                    labels = formatter(nsmall = 1)) +
  theme_bw() +
  theme(strip.background = element_blank(),
        text = element_text(size = 35),
        axis.text = element_text(colour = "black"),
        legend.title = element_blank(),
        # legend.position = c(0.07, 0.95),
        panel.spacing.x = unit(2, "lines"))
```





```{r}
#Can I compare KC10 and FZH01 to complete the time-series?
comp_kc <- kc_qc %>% 
  filter(site_id == "KC10") %>% 
  select(date, depth, filter_type2, avg_chla_k = avg_chla, sum_k = sum)

comp_fh <- kc_qc %>% 
  filter(site_id == "FZH01") %>% 
  select(date, depth, filter_type2, avg_chla_f = avg_chla, sum_f = sum)

comp <- comp_kc %>% 
  full_join(comp_fh)
```
```{r}
comp %>% 
  filter(!is.na(avg_chla_k)) %>% 
  filter(!is.na(avg_chla_f)) %>%
  ggplot(aes(x = avg_chla_k, y = avg_chla_f)) +
  geom_point(size = 2) +
  ggpubr::stat_cor(aes(label = paste(..rr.label.., ..p.label.., sep = "~`,`~")),
                   p.accuracy = 0.001, size = 9) +
  labs(x = bquote(Chla[KC10] ~ "("*mg~m^-3*")"),
       y = bquote(Chla[FZH01] ~ "("*mg~m^-3*")")) +
  facet_wrap(~filter_type2, scales = "free") +
  theme_bw() +
  theme(text = element_text(size = 30), #35
        axis.text = element_text(color = "black"))

ggsave(here("figures", "comparison.png"),
        width = 14, height = 6, dpi = 300)
```

```{r}
clim_m <- kc_qc %>% 
  group_by(month, depth, filter_type2) %>%
  summarise(med_sf = median(avg_chla),
            n = n()) %>% 
  ungroup()

clim_y <- kc_qc %>% 
  group_by(year, depth, filter_type2) %>%
  summarise(med_sf = median(avg_chla),
            n = n()) %>% 
  ungroup() 
```
```{r}
#Looking at monthly medians by filter type and depth
clim_m %>%
  ggplot() +
  geom_bar(aes(x = as.factor(month), y = med_sf, fill = filter_type2),
           position = "stack", stat = "identity") +
  ggsci::scale_fill_d3() +
  facet_grid(depth ~ ., scales = "free_y") +
  theme_bw() +
  labs(y = bquote("Size Fractionated Chla (mg" ~ m^-3*")"),
       fill = "Group") +
  theme(legend.position = "top",
        legend.direction = "horizontal",
        legend.title = element_blank(),
        text = element_text(size = 35), #35
        axis.text = element_text(color = "black"),
        axis.title.x = element_blank()) +
  guides(fill = guide_legend(nrow = 1, reverse = TRUE))

ggsave(here("figures", "climatology_monthly.png"),
        width = 16, height = 14, dpi = 300)
```
```{r}
#Looking at annual medians by depth, but I don't think this really shows much.
clim_y %>%
  ggplot() +
  # geom_area() +
  geom_bar(aes(x = as.factor(year), y = med_sf, fill = filter_type2),
           position = "stack", stat = "identity") +
  # geom_smooth(aes(x = date, y = sum, color = as.factor(year)),
  #             method = "loess", span = 0.05) +
  ggsci::scale_fill_d3() +
  facet_grid(depth ~ ., scales = "free_y") +
  # scale_x_date(breaks = seq(as.Date("2014-01-01"), as.Date("2025-01-01"),
  #                           by = "1 year"), date_minor_breaks = "1 month",
  #              expand = c(0, 0),
  #              date_labels = "%b%y",
  #              limits = c(as.Date("2014-01-01"), as.Date("2025-01-01"))) +
  theme_bw() +
  labs(y = bquote("Size Fractionated Chla (mg" ~ m^-3*")"),
       fill = "Group") +
  theme(legend.position = "top",
        legend.direction = "horizontal",
        legend.title = element_blank(),
        text = element_text(size = 35), #35
        axis.text = element_text(color = "black"),
        axis.title.x = element_blank()) +
  guides(fill = guide_legend(nrow = 1, reverse = TRUE))

ggsave(here("figures", "climatology_yearly.png"),
        width = 16, height = 14, dpi = 300)
```

```{r}
kc_bulk %>% 
  filter(depth < 31) %>% 
  ggplot(aes(x = date, y = bulk, color = site_id)) +
  # geom_area() +
  geom_line(size = 2) +
  geom_point(pch = 21, fill = "white", size = 2) +
  ggsci::scale_fill_d3() +
  facet_grid(depth ~ ., scales = "free_y") +
  scale_x_date(breaks = seq(as.Date("2014-01-01"), as.Date("2025-01-01"),
                            by = "1 year"), date_minor_breaks = "1 month",
               expand = c(0, 0),
               date_labels = "%b%y",
               limits = c(as.Date("2014-01-01"), as.Date("2025-01-01"))) +
  theme_bw() +
  labs(y = bquote("Size Fractionated Chla (mg" ~ m^-3*")"),
       fill = "Group") +
  theme(legend.position = c(0.5, 0.95),
        legend.direction = "horizontal",
        legend.title = element_blank(),
        text = element_text(size = 35), #35
        axis.text = element_text(color = "black"),
        axis.title.x = element_blank()) +
  guides(fill = guide_legend(nrow = 1, reverse = TRUE))

ggsave(here("figures", "timeseries_bulk.png"), 
        width = 16, height = 14, dpi = 300)
```




Ideas

I think the idea is to try to find large-scale linkages with things like ENSO etc.

How many in-situ samples can I leverage across space and time. Maybe this isn't relevent as there is so much inconsistency. Wiley's idea is to use satellite.

If I focus on KC10, can the size-fractionated data highlight some differences in years and depths, potentially through clustering or ordinations. Is it possible that heatwave years had more smaller species or less biomass?

What about fluorescence profiles and integrated chlorophyll? This would give the depth aspect not covered by satellite imagery.

Clean up the KC10 buoy fluorescence records to get a good idea on temporal variability with freshwater, temperature and PAR links? I think 2021, 2022 and 2024 are salvageable, although 2022 needs major spike removal. Is there a point in this though, with Wiley being able to pick up a lot of this information using the CO2 data?



